Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-19 paper.tex
Rewrite AoU results section

The compression was done on a single compute node with 64 CPUs and 416 GiB of RAM.
We first converted the VCF to and ICF, which required 6h17min effective runtime and
343 hours CPU time (parallel efficiency of 86\%), for a cost of \$23.88. The ICF 
representation used a total of 7.5 GiB over 91,232 data storage files. We then 
converted the ICF to Zarr (effective runtime: 50min32s, CPU time: 49h49min, 
parallel efficiency: 92\%, cost: \$3.19), consuming a total of 13 GiB storage 
over 36,9656 chunk files.

>>>>

The compression was performed on a single compute node with 64 CPUs and 416 GiB of RAM.  
We first converted the VCF to an ICF, which took 6 hours and 17 minutes of  
effective runtime and utilized 343 hours of CPU time, achieving a parallel efficiency of 86\%.  
This step incurred a cost of \$23.88. The resulting ICF representation required 7.5 GiB of storage  
distributed across 91,232 files. Next, the ICF was converted to Zarr, which took 50 minutes and 32 
seconds of effective runtime and 49 hours and 49 minutes of CPU time, with a parallel efficiency of 92\%, 
at a cost of \$3.19. The final Zarr representation occupied 13 GiB of storage across 369,656 chunk files.
